Test if analytic derivation of geodesic distance for curves from sim_functional_data.R

### 2019-06-25 test_analytic_geodesic_distance.Rmd
fixed reg_sampling to mean concentrated sampling

```{r}
# Generate data
sim <- sim_functional_data(sce=4,samplesize=1500,K=150,plot_true=1)
```

>>>>

TODO: The reg_sampling parameter in sim_functional_data is somewhat of a misnomer. In either case when it's 0 or 1, it does NOT mean that the manifold can be sampled evenly. Recall swiss roll euclidean example. A simple sampling of the one-dimensional manifold parameter does not mean that entire swiss roll is visited, some corners are seldom sampled. This will affect downstream Floyd's algorithm. Indeed, Diaconis et. al in "Sampling from a Manifold" realize the drawbacks of naive sampling of Euclidean manifolds.

```{r}
# Generate data
sim <- sim_functional_data(sce=4,samplesize=200,K=100,plot_true=1,reg_sampling=0)
```
